\cvsection{Experience}
\begin{cventries}
    \cventry{Software Engineer \& Analyst}
        {Applied Value Group}
        {New York, NY, USA}
        {Sep. 2014 - Jun. 2015, Jun. 2017 - Now}
        {\begin{cvitems}
            \item{Initially worked as an analyst and used Python to perform financial analysis relevant to their consulting business.}
            \item{Wrote Python programs to automate the process of scraping business data and storing it in databases for use with internal and client web apps.}
            \item{Came back to work as a full-stack developer in 2017, working on their internal business intelligence APIs using Flask, Express, MariaDB and MongoDB.}
            \item{Worked on their platform's associated web apps using React, Redux and D3.}
            \item{Apps I worked on included interfaces for data dashboards, visualizations, forms and controls to request newly calculated or parsed results based on input.}
            \item{Deployed platforms on Google Cloud and Digital Ocean using Docker and Kubernetes.}
        \end{cvitems}}
    \cventry{Software Engineer}
        {Method Inc.}
        {New York, NY, USA}
        {May. 2015 - Jun. 2016}
        {\begin{cvitems}
            \item{Following the Flatiron School iOS bootcamp I was hired to work on various feature updates and bugfixes for their contracted app for McDonalds.}
            \item{Created native app views for their purchasing, locator, and deals features of the McDonalds app.}
            \item{Learned React and React Native to help with other contracted teams that wanted cross platform apps.}
            \item{Collaborated with designers to create, in software, the design wireframes they had come up with.}
            % \item{Helped develop a backend application for their UX showcase demonstrations that was used to map rendered interfaces on different displays.}
        \end{cvitems}}
    \cventry{Embedded Software Developer Intern}
        {ABB Inc.}
        {Västerås, Sweden}
        {Sep. 2012 \- Mar. 2013}
        {\begin{cvitems}
            \item{Wrote scripts in bash on automation servers to test hardware and robotic environment. Adding old test functionality to their new operating system.}
            \item{Added and tested event-driven interrupt routines in C++ and their own proprietary `RAPID' language, to improve safety of pick-place robots on new family of controllers that halt the system if there are safety concerns that it can detect.}
            \item{Helped develop libraries in C++ that ported functionality of old controller operating system to a new one that was being released.}
        \end{cvitems}}

    % \cventry{Electronics Engineer Intern}
    %     {Sony Ericsson (Currently Sony Mobile)}
    %     {Lund, Sweden}
    %     {May 2011 \- Aug. 2011}
    %     {\begin{cvitems}
    %         \item{Tested and debugged manufacturing samples of different mobile circuit boards to help team find areas where either the design of the boards could improve or the manufacturing process, which ended in two design revisions.}
    %         \item{Designed and created a regulator testing device that could log voltage regulator transient response under different load conditions, improving the team's ability to quickly diagnose power conditioning problems of engineering sample boards.}
    %         \end{cvitems}
    %     }

%    \cventry{Electronics Engineering Intern}
%        {Redback Networks (Acquired by Ericsson)}
%        {San Jose, CA, USA}
%        {Jun. 2010 \- Aug. 2010}
%        {\begin{cvitems}
%          \item{Helped Design and test logic shifters, regulators and fan controllers for their networking products.}
%      \end{cvitems}
%  }
\end{cventries}
