%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Major Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {An iOS app that acts as a gateway to all your communications apps}
    {Hub} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems}
        \item {Links to phone app, texting app, e-mail, Facebook, LinkedIn, and twitter.}
        \item {Acts as all-in-one communication app for all bookmarked contacts using all the communication methods described above.}
        \item {Programmed in Swift, using these frameworks: CoreData, Facebook SDK, STTwitter, AFNetworking, CNContacts, CloudKit, UIKit}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {App that tracks users using the MTA for more accurate timing}
    {SubWaze} % Organization/group
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Tracks users using New York's MTA subway using geo-fences or manual interaction to keep an up-to-date cloud based time table of the MTA's trains.}
        \item {Programmed in Objective C, using these frameworks: CoreData, GTFS, Protocol Buffers, Parse, CoreLocation, CoreGraphics, UIKit}
        \item {Conducted periodic security checks on overall IT system as a member of POSTECH CERT.}
        \item {Conducted penetration testing commissioned by national agency and corporation.}
      \end{cvitems}
    }
%---------------------------------------------------------

    \cventry
      {A to-do list manager}
      {Just.Do}
      {}
      {}
      {
        \begin{cvitems}
          \item {A basic to-do list with sliding table cells and custom animations taken from cocoa pods.}
          \item {Written in Objective C using UIKit, CoreData, and MCSwipeTableViewCell}
          \end{cvitems}
      }

%---------------------------------------------------------

    \cventry
      {A whack-a-mole style iOS game}
      {Whack-a-Doge}
      {}
      {}
      {
        \begin{cvitems}
          \item {Users advance the games difficulty and background scenes by tapping doge pictures that pop up on screen}
          \item {Written in Objective C using SpriteKit}
        \end{cvitems}
      }

%---------------------------------------------------------

    \cventry
      {Capstone research project for RIT's Multi-Agent Biorobotics Lab (MABL)}
      {Simultaneous Localization And Mapping (SLAM) Robot}
      {}
      {}
      {
        \begin{cvitems}
          \item {A robot that uses SLAM with a Kalman Filter that could map and localize itself with only time-of-flight sensors(sonar), and dead-reckoning.}
          \item {Written in C++ \& MATLAB using the AmigoBot robot platform.}
          \end{cvitems}
      }

%---------------------------------------------------------
    \cventry
      {Capstone research project for RIT's Multi-Agent Biorobotics Lab (MABL)}
      {Simultaneous Localization And Mapping (SLAM) Robot}
      {} % Location
      {} % Date(s)
      {
        \begin{cvitems}
          \item {A robot that uses SLAM with a Kalman Filter that could map and localize itself with only time-of-flight sensors(sonar), and dead-reckoning.}
          \item {Written in }
        \end{cvitems}
      }


%---------------------------------------------------------
\end{cventries}

%Forget Me Not
  %+ An app that helps track how much and how often you communicate with %bookmarked people from the phone's address book and/or linked social accounts, %and reminds you to correspond with them at some desired .
  %+ Links to phone app, texting app, e-mail, Facebook, LinkedIn, and twitter.
  %+ Acts as all-in-one communication app for all bookmarked contacts using all %the communication methods described above
  %+ Programmed in Swift, using these frameworks: CoreData, %Facebook SDK, STTwitter, AFNetworking, CNContacts, CloudKit, UIKit
%Crowd Sourced Subway Timing App
%  + Tracks users using New York's MTA subway using geo-fences or manual interaction to keep an up-to-date cloud based time table of the MTA's trains at each station updated by any user of the app
%  + Programmed in Objective C, using these frameworks: CoreData, GTFS, Protocol %Buffers, Parse, CoreLocation, CoreGraphics, UIKit
%Whack-a-Doge
  %+ A strange and silly whack-a-mole style game on the iPhone.
  %+ Written in Objective C using mostly just SpriteKit
%Simultaneous Localization And Mapping (SLAM) Robot
%  + Capstone research project for RIT's Multi-Agent Biorobotics Lab (MABL)
%  + A robot that uses SLAM with a Kalman Filter that could map and localize %itself with only time-of-flight sensors.
%  + Written in C++ & MATLAB and uses the AmigoBot robot platform.
%  + Include Link to project.
